---
title: "JSC270 - Laboratories Documents"
output: 
  html_document:
   toc: true
   toc_depth: 3
   toc_float: true
   theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
```

<br>
<br>


# Laboratory \#1

<br> 

#### Overview

- [Lab 1: Overview of the laboratory](https://jsc270.github.io/labs/L1.html)

<br>

#### Questions and starter code

- [Lab 1.0: Pre-lab Questions](https://jsc270.github.io/labs/L1.0.html)  

- [Lab 1.1: Lab Assignment](https://jsc270.github.io/labs/L1.1.html) 

- [Lab 1.2: Reflections](https://jsc270.github.io/labs/L1.2.html) 

<br> 

#### Resources 

- [Pandas Cheat Sheet](docs/Pandas_Cheat_Sheet.pdf) ([see ref](https://github.com/pandas-dev/pandas))

- [Pandas project](https://pandas.pydata.org)

- [git Basics](docs/jsc270-git-basics.pdf)


<br>

# Laboratory \#2

<br> 

#### Overview

- [Lab 2: Overview of the laboratory](https://jsc270.github.io/labs/L2.html)

<br>

#### Questions and starter code

- [Lab 2.0: Pre-lab Questions](https://jsc270.github.io/labs/L2.0.html)  

- [Lab 2.1: Lab Assignment](https://jsc270.github.io/labs/L2.1.html) 

- [Lab 2.2: Reflections](https://jsc270.github.io/labs/L2.2.html) 

<br> 

# Laboratory \#3

<br> 

#### Overview

- [Lab 3: Overview of the laboratory](https://jsc270.github.io/labs/L3.html)

<br>

#### Questions and starter code

- [Lab 3.0: Pre-lab Questions](https://jsc270.github.io/labs/L3.0.html)  

- [Lab 3.1: Lab Assignment](https://jsc270.github.io/labs/L3.1.html) 

- [Lab 3.2: Reflections](https://jsc270.github.io/labs/L3.2.html) 


<br> 

# Laboratory \#4

<br> 

#### Overview

- [Lab 4: Overview of the laboratory](https://jsc270.github.io/labs/L4.html)

<br>

#### Questions and starter code

- [Lab 4.0: Pre-lab Questions](https://jsc270.github.io/labs/L4.0.html) 

- [Lab 4.1: Lab Assignment](https://jsc270.github.io/labs/L4.1.html) 

- [Lab 4.2: Reflections](https://jsc270.github.io/labs/L4.2.html) 


<br> 

# Laboratory \#5

<br> 

#### Overview

- [Lab 5: Overview of the laboratory](https://jsc270.github.io/labs/L5.html)

<br>

#### Questions 

- [Lab 5.0: Pre-lab Assignment](https://jsc270.github.io/labs/L5.0.html) 

- [Lab 5.1: In-lab Presentation](https://jsc270.github.io/labs/L5.1.html) 

- [Lab 5.2: Reflections](https://jsc270.github.io/labs/L5.2.html) 


<br> 

# Laboratory \#6

<br> 

#### Overview

- [Lab 6: Overview of the laboratory](https://jsc270.github.io/labs/L6.html)

<br>

#### Questions 

- [Lab 6.0: Pre-lab Assignment](https://jsc270.github.io/labs/L6.0.html) 

- [Lab 6.1: In-lab Assignment](https://jsc270.github.io/labs/L6.1.html) 

- [Lab 6.2: Reflections](https://jsc270.github.io/labs/L6.2.html)


<br> 


# Laboratory \#7

<br> 


#### Questions 

- [Lab 7.0: Pre-lab Assignment](https://jsc270.github.io/labs/L7.0.html) 

- [Lab 7.1: In-lab Assignment](https://jsc270.github.io/labs/L7.1.html) 

- [Lab 7.2: Reflections](https://jsc270.github.io/labs/L7.2.html) 



<br> 


# Practice Laboratory (A3)


<br> 

- [A3 sandbox notebook](https://jsc270.github.io/labs/A3-sandbox.html) 



<!--- <br>

****

# Tutorial Schedule

The following is a tentative schedule, subject to change slightly.

```{r, echo=FALSE}
jsc270_tutsched <- read_csv("tut_sched.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_tutsched)
```

--->