---
title: "JSC270 - Class Documents"
output: 
  html_document:
   toc: true
   toc_depth: 3
   toc_float: true
   theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F, message = F)
```

<br>


Documents from class will be posted on this page.

<br>

# Class 1 - Wednesday January 9

[Prof. Taback's notebook](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class1/Class1.ipynb)

[Prof. Chevalier's notebook](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class1/Class1-Part2.ipynb)

[Prof. Chevalier's notebook - in-class use case](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class1/Class1-EDA_OkCupid.ipynb)

<br>

# Class 2 - Monday, January 14

[Prof. Taback's notebook](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)

**NB: If you are installing [`omdb` python library](https://pypi.org/project/omdb/) using Jupyter notebook use the command in a Jupyter code cell: `!pip install --user omdb` (i.e., make sure to include the user flag).  Alternatively, you can run the command from the terminal.**

<br>

# Class 3 - Monday, January 21

[Prof. Chevalier's notebook (student version for class)](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class3/lecture3_slides-students.ipynb)

[Prof. Chevalier's notebook (complete version with solutions and comments)](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class3/lecture3_slides-complete.ipynb)

Datasets used in class 3:

- [Movies dataset](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class3/data/50movies-clean.csv)

- [Titanic dataset](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class3/data/titanic.csv)

<br>

# Class 4 - Monday January 28

[Class slides](https://github.com/JSC270/JSC270.github.io/tree/master/notebooks/class4)

### Readings

- [The Surprising Power of Online Experiments](https://hbr.org/2017/09/the-surprising-power-of-online-experiments)

- [Why Donald Trump is the political equivalent of a Silicon Valley startup](https://theweek.com/articles/626366/why-donald-trump-political-equivalent-silicon-valley-startup)

- [Randomization and Bias in Cancer Clinical Trials](https://www.cancer.gov/about-cancer/treatment/clinical-trials/what-are-trials/randomization)

<br>

# Class 5 - Monday February 4

[Class slides](https://github.com/JSC270/JSC270.github.io/tree/master/notebooks/class5)

<br>

# Class 6 - Monday February 11

[Class slides](https://github.com/JSC270/JSC270.github.io/tree/master/notebooks/class6)

### Reading

[An An Introduction to Statistical Learning with Applications in R](http://www-bcf.usc.edu/~gareth/ISL/).  The material from today's class is scattered over chapters 2, 3, 4, 5, 6, 8.  

<br>

# Class 7 - Monday February 25

[Class slides](https://github.com/JSC270/JSC270.github.io/tree/master/notebooks/class7/lecture7.pdf)

### Readings

- [Preattentive processing in vision](https://www-sciencedirect-com.myaccess.library.utoronto.ca/science/article/pii/S0734189X85800049) -- Available on UofT network and through UofT library

- [The value of Information Visualization](https://www.win.tue.nl/~vanwijk/infovis_springer.pdf)

- [The good, the bad, and the biased: five ways visualization can mislead](http://interactions.acm.org/archive/view/july-august-2018/the-good-the-bad-and-the-biased)


<br>

# Class 8 - Monday March 11

[Class slides](https://github.com/JSC270/JSC270.github.io/tree/master/notebooks/class8/lecture8.pdf)


<br>

# Class 9 - Monday March 18

[Prof. Ahmed's slides](https://docs.google.com/presentation/d/1TuDVBKXjULkA7x7pKLt-mdVIzyG5civqwD1rXFmjMtk/edit#slide=id.p)


<br>

# Class 10 - Monday March 25

[Class slides](https://github.com/JSC270/JSC270.github.io/tree/master/notebooks/class10/JSC270-Class10.pdf)


<br>


******

# Python References


- [seaborn documentation](https://seaborn.pydata.org/)

- [matplotlib documentation](https://matplotlib.org/)

- [pandas documentation](http://pandas.pydata.org/pandas-docs/stable/)

- Python Data Analytics: Data Analysis and Science Using Pandas, matplotlib, and the Python Programming Language, by Fabio Nelli. (Chapters 4 - 7) [Electronic copy available from UofT library](http://go.utlib.ca/cat/10190695)

<br>

******

# Class Schedule

```{r, echo=FALSE}
library(tidyverse)
jsc270_classsched <- read_csv("jsc270_class_sched.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_classsched)
```

