---
title: "JSC270 - Class Documents"
output: 
  html_document:
   toc: true
   toc_depth: 3
   toc_float: true
   theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F, message = F)
```

<br>


Documents from class will be posted on this page.

<br>

# Class 1 - Monday January 6


<br>


<br>


******

# Python References


- [seaborn documentation](https://seaborn.pydata.org/)

- [matplotlib documentation](https://matplotlib.org/)

- [pandas documentation](http://pandas.pydata.org/pandas-docs/stable/)

- Python Data Analytics: Data Analysis and Science Using Pandas, matplotlib, and the Python Programming Language, by Fabio Nelli. (Chapters 4 - 7) [Electronic copy available from UofT library](http://go.utlib.ca/cat/10190695)

<br>

******

# Class Schedule

The following is a tentative schedule, subject to change slightly.

```{r, echo=FALSE}
library(tidyverse)
jsc270_classsched <- read_csv("class_sched.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_classsched)
```

