---
title: "JSC270 - Class Documents"
output: 
  html_document:
   toc: true
   toc_float: true
   theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F, message = F)
```

<br>


# Class Documents

Documents from class will be posted on this page.

## Class 1 - Wednesday, January 9

[Prof. Taback's notebook](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class1/Class1.ipynb)

[Prof. Chevalier's notebook](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class1/Class1-Part2.ipynb)

[Prof. Chevalier's notebook - in-class use case](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class1/Class1-EDA_OkCupid.ipynb)

## Class 2 - Monday, January 14

[Prof. Taback's notebook](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)

**NB: If you are installing [`omdb` python library](https://pypi.org/project/omdb/) using Jupyter notebook use the command in a Jupyter code cell: `!pip install --user omdb` (i.e., make sure to include the user flag).  Alternatively, you can run the command from the terminal.**


## Class 3 - Monday, January 21

[Prof. Chevalier's notebook (student version for class)](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class3/lecture3_slides-students.ipynb)

[Prof. Chevalier's notebook (complete version with solutions and comments)](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class3/lecture3_slides-complete.ipynb)

Datasets used in class 3:

- [Movies dataset](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class3/data/50movies-clean.csv)

- [Titanic dataset](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class3/data/titanic.csv)



<br>

******

# References


- [seaborn documentation](https://seaborn.pydata.org/)

- [matplotlib documentation](https://matplotlib.org/)

- [pandas documentation](http://pandas.pydata.org/pandas-docs/stable/)

- Python Data Analytics: Data Analysis and Science Using Pandas, matplotlib, and the Python Programming Language, by Fabio Nelli. (Chapters 4 - 7) [Electronic copy available from UofT library](http://go.utlib.ca/cat/10190695)

<br>

******

# Class Schedule

```{r, echo=FALSE}
library(tidyverse)
jsc270_classsched <- read_csv("jsc270_class_sched.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_classsched)
```

