---
title: "JSC270 - Laboratories Documents"
output: 
  html_document:
   toc: true
   toc_depth: 3
   toc_float: true
   theme: yeti
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
```

<br>
<br>
This is the section for Tutorial Labs. These labs will be held on Wednesdays, from 12-2pm on Zoom. The link and password can be found on Quercus. The goal of these Labs is to teach students how to implement the theory they learn in lecture. After each lab, the code (and any other relevant files) will be posted below. See the class schedule for a tentative list of the Lab topics. 


## Lab 1 - Jan 13

Here is the code for Tutorial 1: <a href="https://colab.research.google.com/drive/1pMK5-wncxvKDsuFQCTPJjdixYK5MVjdM?usp=sharing" target="_blank">Colab Notebook</a>.

This is the recording for Tutorial 1: <a href="https://drive.google.com/file/d/1bFC1mGL-qa7K2HAjM_HResnjXZp6u-r3/view" target="_blank">MP4 File</a>.

<br>

## Lab 2 - Jan 20

Here is the Cars dataset for Tutorial 2: <a href="./datasets/archive.zip">CSV File</a>.

Here is the code: <a href ="https://colab.research.google.com/drive/1SCp5yXNc7rhhDmcLMmsEBPTcB7arMNYw?usp=sharing" target="_blank">Colab Notebook</a>

This is the recording: <a href="https://drive.google.com/file/d/1EH_OREaBRUZTfMzwFF65ZxL1mkrAJ487/view?usp=sharing" target="_blank">MP4 File</a>

<br>

## Lab 3 - Jan 27

Here are the slides from the first part of the lab: <a href="JSC270.github.io/docs/JSC270-Lab3.pdf" target="_blank">Slides</a>

Here is the code: <a href ="https://colab.research.google.com/drive/1a9ugvVbtnR7Oz1L3yQxJWJ2SawagHb2p?usp=sharing" target="_blank">Colab Notebook</a>

Here is the recording: <a href="https://drive.google.com/file/d/11mOQPW8hSae_sRjfosOZum30XlSW4Xud/view?usp=sharing" target="_blank">MP4 File</a>

<br>

## Lab 4 - Feb 3
Here are today's slides on Git and Bash:  <a href="JSC270.github.io/docs/git-bash-slides.pdf" target="_blank">PDF</a>

Here is the recording: <a href="https://drive.google.com/file/d/1wB55_DgI7NkisGPsX379tdUWlA1PhiH3/view?usp=sharing" target="_blank">MP4 File</a>

<br> 

## Lab 5 - Feb 10

Here is the lab notebook on simulation: <a href="https://colab.research.google.com/drive/16MIUuVSw5q2F8QDkzHNU9mu9-IaMX5p7?usp=sharing" target="_blank">Colab Notebook</a>

Here is the recording for part I: <a href="https://drive.google.com/file/d/1Gl_Wsj5R-F707urKtoBpK1Yh1kAK_gsq/view?usp=sharing" target="_blank">MP4 File</a>

Here is the recording for part II: <a href="https://drive.google.com/file/d/1bwhfqcwzkAhU60bxDM7uWvhyZ6CEaxW1/view?usp=sharing" target="_blank">MP4 File</a>

<br>

## Lab 6 - Feb 24

Here is the notebook for `numpy` (Part I): <a href="https://colab.research.google.com/drive/1tpNMLACA8_8lqwnU13wxSvwmPPjHIxyL?usp=sharing" target="_blank">Colab Notebook</a>

Here is the notebook for `scikit-learn` (Part II): <a href="https://colab.research.google.com/drive/1Jk1_s7qR7IdE2gnqqD2pZ5yO-K7t7voe?usp=sharing" target="_blank">Colab Notebook</a>

Here is the recording: <a href="https://drive.google.com/file/d/1gai970OsKv1FfGv65hqLUkq1RZO7b9Ul/view?usp=sharing" target="_blank">MP4 File</a>

<br>

## Lab 7 - Mar 3rd

Here is a link to the git repo for this lab: <a href="https://github.com/larunerdman/JSC270_Lab7" target="_blank">GitHub</a>

Here is the recording: <a href="https://drive.google.com/file/d/1clctHp933PCeP5VBRUG9-6ggEsBC9FZj/view?usp=sharing" target="_blank">MP4 File</a>

<br>

# Lab 8 - Mar 10th

Here is the NLP notebook (part I): <a href="https://colab.research.google.com/drive/15VzAybbRK2qmXfA3_PFeL22NpGyYNfik?usp=sharing" target="_blank">Colab Notebook</a>

Here is the spam dataset for Part I: <a href="./datasets/spam.csv">CSV File</a>.

Here is the notebook on the Twitter API (part II): <a href="https://colab.research.google.com/drive/1zSlUQbrysSnibrumNIPK5Ul7H0aa8oeF?usp=sharing" target="_blank">Colab Notebook</a>

<!--- <br>

****

# Tutorial Schedule

The following is a tentative schedule, subject to change slightly.

```{r, echo=FALSE}
jsc270_tutsched <- read_csv("tut_sched.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_tutsched)
```

--->
