---
title: "JSC270 - Tutorial Documents"
output: 
  html_document:
   toc: true
   toc_float: true
   theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
```

<br>

# Tutorial Documents

# Tutorial 0 - Monday, January 7

[Questions for Tutorial 0](tutorials/Tutorial0HelloJSC270.html)

[Answers to Tutorial 0 Questions](tutorials/Tutorial0HelloJSC270-answers-posted.html)

# Tutorial 1 - Wednesday, January 16

Questions for Tutorial 1: [html](tutorials/jsc270_tut1_questions.html); [ipynb](https://github.com/JSC270/JSC270.github.io/blob/master/tutorials/jsc270_tut1_questions.ipynb)

## Resources for Tutorial 1

- [Pandas Cheat Sheet](Pandas_Cheat_Sheet.pdf) ([see ref](https://github.com/pandas-dev/pandas))

- [Pandas project](https://pandas.pydata.org)

- [The Truth About Algorithms, Cathy O'Neil](https://youtu.be/heQzqX35c9A)

A few articles on hiring algorithms: 

- [Hiring Algorithms Are Not Neutral - Harvard Business Review](https://hbr.org/2016/12/hiring-algorithms-are-not-neutral)

- [A.I. as Talent Scout: Unorthodox Hires, and Maybe Lower Pay - New York Times](https://www.nytimes.com/2018/12/06/business/economy/artificial-intelligence-hiring.html)

- [Amazon scraps secret AI recruiting tool that showed bias against women - Reuters](https://www.reuters.com/article/us-amazon-com-jobs-automation-insight/amazon-scraps-secret-ai-recruiting-tool-that-showed-bias-against-women-idUSKCN1MK08G)




<br>


# Tutorial Grading

```{r}
tutorial_rubric <- read_csv("rubrics/tutorial_rubric.csv")
knitr::kable(tutorial_rubric)
```


<br>

# Tutorial Schedule

```{r, echo=FALSE}
jsc270_tutsched <- read_csv("jsc270_tutsched.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_tutsched)
```
