---
title: "JSC270 - Laboratories Documents"
output: 
  html_document:
   toc: true
   toc_depth: 3
   toc_float: true
   theme: yeti
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
```

<br>
<br>
This is the section for Tutorial Labs. These labs will be held on Wednesdays, from 12-2pm on Zoom. The link and password can be found on Quercus. The goal of these Labs is to teach students how to implement the theory they learn in lecture. After each lab, the code (and any other relevant files) will be posted below. See the class schedule for a tentative list of the Lab topics. 


## Lab 1 - Jan 13

Here is the code for Tutorial 1: <a href="https://colab.research.google.com/drive/1pMK5-wncxvKDsuFQCTPJjdixYK5MVjdM?usp=sharing" target="_blank">Colab Notebook</a>.

This is the recording for Tutorial 1: <a href="https://drive.google.com/file/d/1bFC1mGL-qa7K2HAjM_HResnjXZp6u-r3/view" target="_blank">MP4 File</a>.

## Lab 2 - Jan 20

Here is the Cars dataset for Tutorial 2: <a href="./datasets/Automobile_data.csv">CSV File</a>.

## Lab 3 - Jan 27

## Lab 4 - Feb 3

<br> 

<!--- <br>

****

# Tutorial Schedule

The following is a tentative schedule, subject to change slightly.

```{r, echo=FALSE}
jsc270_tutsched <- read_csv("tut_sched.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_tutsched)
```

--->
