---
title: "JSC270 - Tutorial Documents"
output: 
  html_document:
   toc: true
   toc_depth: 3
   toc_float: true
   theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
```

<br>
<br>

# Tutorial 0 - Mon. January 7

[Questions for Tutorial 0](tutorials/Tutorial0HelloJSC270.html)

[Answers to Tutorial 0 Questions](tutorials/Tutorial0HelloJSC270-answers-posted.html)

<br>

# Tutorial 1 - Wed. January 16

Questions for Tutorial 1: [html](tutorials/jsc270_tut1_questions.html); [ipynb](https://github.com/JSC270/JSC270.github.io/blob/master/tutorials/jsc270_tut1_questions.ipynb)

### Resources for Tutorial 1

- [Pandas Cheat Sheet](Pandas_Cheat_Sheet.pdf) ([see ref](https://github.com/pandas-dev/pandas))

- [Pandas project](https://pandas.pydata.org)

- [git Basics](tutorials/jsc270-git-basics.pdf)

- [The Truth About Algorithms, Cathy O'Neil](https://youtu.be/heQzqX35c9A)

A few articles on hiring algorithms: 

- [Hiring Algorithms Are Not Neutral - Harvard Business Review](https://hbr.org/2016/12/hiring-algorithms-are-not-neutral)

- [A.I. as Talent Scout: Unorthodox Hires, and Maybe Lower Pay - New York Times](https://www.nytimes.com/2018/12/06/business/economy/artificial-intelligence-hiring.html)

- [Amazon scraps secret AI recruiting tool that showed bias against women - Reuters](https://www.reuters.com/article/us-amazon-com-jobs-automation-insight/amazon-scraps-secret-ai-recruiting-tool-that-showed-bias-against-women-idUSKCN1MK08G)

<br>

# Tutorial 2 - Wed. January 23

Questions for Tutorial 2: [html](tutorials/jsc270_tut2_student.html); [ipynb](https://github.com/JSC270/JSC270.github.io/blob/master/tutorials/jsc270_tut2_student.ipynb)

<br>

# Tutorial 3 - Wed. January 30 

Questions for Tutorial 3: [html](tutorials/jsc270_tut3_student.html); [ipynb](tutorials/jsc270_tut3_student.ipynb)

### Resources for Tutorial 3

- [ipywidgets library](https://ipywidgets.readthedocs.io)

- [Survey Research (in psychology)](https://web.stanford.edu/dept/communication/faculty/krosnick/Survey_Research.pdf)

- [Survey Research in HCI](https://link-springer-com.myaccess.library.utoronto.ca/chapter/10.1007/978-1-4939-0378-8_10)

- [Likert scales: how to (ab)use them](https://pdfs.semanticscholar.org/3ebe/1b5c7e927be0221788348973b17c9de3bf05.pdf)


<br>

# Tutorial 4 - Wed. February 13

Homework to be completed for Tutorial 4.   

## Part 1: Tell us a story! (Communication exercise) 

- [html](tutorials/jsc270_tut4_part1_questions.html)

- [Presentation rubric](tutorials/tutorial4-presentation-rubric.pdf)

## Part 2: Statistical inference

- [ipynb](https://github.com/JSC270/JSC270.github.io/blob/master/tutorials/jsc270_tut4_part2_questions.ipynb) 

<br>


# Tutorial 5 - Wed. Feb 27

A2 presentations.

<br>

# Tutorial 6 - Wed. March 6

[Questions](tutorials/tutorial6.html)

<br>


# Tutorials 7 and 8 - March 20 and March 27

[Presentation instructions](tutorials/tutorial7-8.html)

<br>
<br>
 ******


# Tutorial Grading

```{r}
tutorial_rubric <- read_csv("rubrics/tutorial_rubric.csv")
knitr::kable(tutorial_rubric)
```


 ******

<br>

# Tutorial Schedule

```{r, echo=FALSE}
jsc270_tutsched <- read_csv("jsc270_tutsched.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_tutsched)
```
