---
title: "JSC270 - Tutorial Documents"
output: 
  html_document:
   toc: true
   toc_depth: 3
   toc_float: true
   theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
```

<br>
<br>


# Tutorial 1

* [Tutorial Overview]() 
    + [Tutorial 1.0: Pre-lab Questions]()  
    + [Tutorial 1.1: Tutorial Assignment]() 
    + [Tutorial 1.2: Reflections]() 
<br> 

#### Resources for Tutorial 1

- [Pandas Cheat Sheet](docs/Pandas_Cheat_Sheet.pdf) ([see ref](https://github.com/pandas-dev/pandas))

- [Pandas project](https://pandas.pydata.org)

- [git Basics](docs/jsc270-git-basics.pdf)


<br>



<br>
<br>
 ******


# Tutorial In-Lab Progress Grading

```{r}
tutorial_rubric <- read_csv("rubrics/labprogress_rubric.csv")
knitr::kable(tutorial_rubric) 
```

# Tutorial Assignment Completion Grading


```{r}
tutorial_rubric <- read_csv("rubrics/tutorial_rubric.csv")
knitr::kable(tutorial_rubric) 
```

# Tutorial Reflections Grading

```{r}
tutorial_rubric <- read_csv("rubrics/reflections_rubric.csv")
knitr::kable(tutorial_rubric)
```

 ******

<br>

# Tutorial Schedule

The following is a tentative schedule, subject to change slightly.

```{r, echo=FALSE}
jsc270_tutsched <- read_csv("tut_sched.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_tutsched)
```
