---
title: ""
output: 
  html_document:
   toc: true
   toc_float: true
   theme: yeti
---

```{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(warning = F, message = F)
```
<br>

# <span class="glyphicon glyphicon-calendar" aria-hidden="false"></span> Course Schedule
Below is our course schedule, which may change as the course progresses.  Details regarding evaluation due dates can be found below the table.

```{r, echo=FALSE}
library(tidyverse)
library(kableExtra)
options(knitr.kable.NA = '')

my_backgrounds <- colorRampPalette(c("white", "gray"))(5)
k <- 9
row_nums <-sort(c(seq(1,39,6), seq(2,39,6), seq(3,39,6)))

jsc270courseschedule <- read_csv("Winter2022_schedule - Website Schedule.csv")
knitr::kable(jsc270courseschedule[1:39,]) %>%  
  kable_styling(full_width = T, position = "float_left")   %>%   
  row_spec(row_nums ,background = my_backgrounds[2]) 
```

<br>

# <span class="glyphicon glyphicon-calendar" aria-hidden="true"></span> Evaluation Details

Assignments and reflection quizzes are to be submitted via Quercus.  Perusall papers are completed within the Perusall application.

The deadline for submission for assignments, Perusall papers, and reflection quizzes is always 10:59am EST on the due date (1 hour before class starts).

<!-- # ```{r, echo=FALSE} -->
<!-- # library(tidyverse) -->
<!-- # library(kableExtra) -->
<!-- # options(knitr.kable.NA = '') -->
<!-- #  -->
<!-- # my_backgrounds <- colorRampPalette(c("white", "gray"))(5) -->
<!-- # k = 6  -->
<!-- # row_nums <-c(rbind(1+4*(0:k), 2+4*(0:k))) -->
<!-- #  -->
<!-- # jsc270courseassschedule <- read_csv("Winter2022_assignment_schedule.csv") -->
<!-- # knitr::kable(jsc270courseassschedule[1:26,])  %>%  -->
<!-- #    kable_styling(full_width = T, position = "float_left")   %>%  -->
<!-- #   row_spec(row_nums,background = my_backgrounds[2])  -->
<!-- # ``` -->

<!-- <br> -->
